TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-07-29 paper/draft.tex
describe 2 catalogs
cut out panel

\begin{figure*}
\begin{center}
	\includegraphics[width=.48\linewidth]{figures/ruwe_cut_before.png}
	\includegraphics[width=.48\linewidth]{figures/ruwe_cut_after.png}
	\caption{The left panel shows the test sample of 8,335 sources after applying Selections $1-3$ described in Section \ref{subsec:test_selection}. The right panel shows the same test sample reduced to 6,221 after applying an astrometric quality cut of ${\rm RUWE}<1.2$ (Selection 4). To further remove sources which were likely binary contamination (Selection 5), we cut out sources above the red line which sparsely lay above the majority of the main-sequence with temperatures and metallicities that deviated from the expected gradient, reducing the final test sample to a size of 5,875 sources. The red line shown is constrained by the coordinates $\left\{ (3.5,12), (1.87,7.5) \right\}$ corresponding to ($BP-RP$, $M_G$).}
	\label{fig:ruwe_cut}
\end{center}
\end{figure*}

@@

Table \ref{table:test_results} outlines the parameters included in the test sample catalog, which can be downloaded from the online journal.

% ----------------------------------------
\subsection{Color-Temperature Comparisons}

\color{gcolor}{As a validation test of our derived temperatures, we perform a comparison between several color-temperature relations from literature, which use combination of \zmass\ and visual band photometries to predict temperatures (similarly to the \citealt{Schmidt:2016} evaluation of ASPCAP temperatures). To obtain visual band magnitudes for a set of sources, we cross-matched the 5,875 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 6,257 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from \apogee. Figure \ref{fig:teff_comparisons} shows \cannon\ vs. photometric temperatures on the right, and ASPCAP vs. photometric temperatures on the left for each of the 6,257 sources, colored by their respective spectroscopic metallicities.

@@

While the large bulk of points falling within the temperature ranges of the plots shown does not qualitatively show a lot more deviation from color-temperature relations, the average ASPCAP temperatures are much hotter, and scatters are much higher skewed by 500 sources which ASPCAP predicts to have temperatures over 4200K.}\color{black}

% ----------------------------------------
\subsection{Isochrone Comparisons}

@@

\begin{figure*}[]
\begin{center}
	\includegraphics[width=.9\linewidth]{figures/aspcap_cannon_validation.png}
	\caption{\cannon\ (right column) and ASPCAP (left column) temperatures as compared to temperatures estimated color-temperature relations from three different literature sources for a subsample of 6,257 sources with $V,J,K$ colors. Shown are \cannon\ and ASPCAP temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and $\feh$ dependent relation (top), \citealt{Casagrande:2008} $V-K$ relation (middle), and the \citealt{Boyajian:2012} relation $V-K$ and $\feh$ (bottom).}
	\label{fig:teff_comparisons}
\end{center}
\end{figure*}

>>>>

\begin{figure}
\begin{center}
	\includegraphics[width=\linewidth]{figures/ruwe_cut_before.png} \\
	\includegraphics[width=\linewidth]{figures/ruwe_cut_after.png}
	\caption{The left panel shows the test sample of 8,335 sources after applying Selections $1-3$ described in Section \ref{subsec:test_selection}. The right panel shows the same test sample reduced to 6,221 after applying an astrometric quality cut of ${\rm RUWE}<1.2$ (Selection 4). To further remove sources which were likely binary contamination (Selection 5), we cut out sources above the red line which sparsely lay above the majority of the main-sequence with temperatures and metallicities that deviated from the expected gradient, reducing the final test sample to a size of 5,875 sources. The red line shown is constrained by the coordinates $\left\{ (3.5,12), (1.87,7.5) \right\}$ corresponding to ($BP-RP$, $M_G$).}
	\label{fig:ruwe_cut}
\end{center}
\end{figure}

\begin{figure*}[]
\begin{center}
	\includegraphics[width=.9\linewidth]{figures/aspcap_cannon_validation.png}
	\caption{\cannon\ (right column) and ASPCAP (left column) temperatures as compared to temperatures estimated color-temperature relations from three different literature sources for a subsample of 1,702 sources with $V,J,K$ colors. Shown are \cannon\ and ASPCAP temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and $\feh$ dependent relation (top), and the \citealt{Boyajian:2012} relation $V-K$ and $\feh$ (bottom).}
	\label{fig:teff_comparisons}
\end{center}
\end{figure*}

@@

Table \ref{table:test_results} outlines the parameters included in the test sample catalog, which can be downloaded from the online journal. Included are two versions of the catalog: the first containing all 14,827 sources before selection, and the second containing the 5,875 sources kept after making Selections $1-5$ described in this section.

% ----------------------------------------
\subsection{Temperature Validation}

As a validation test of our derived temperatures, we perform a comparison between several color-temperature relations from literature, which use combination of \zmass\ and visual band photometries to predict temperatures (similarly to the \citealt{Schmidt:2016} evaluation of ASPCAP temperatures). To obtain visual band magnitudes for a set of sources, we cross-matched the 5,875 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 6,257 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from \apogee. Figure \ref{fig:teff_comparisons} shows \cannon\ vs. photometric temperatures on the right, and ASPCAP vs. photometric temperatures on the left for each of the 6,257 sources, colored by their respective spectroscopic metallicities.

@@

% ----------------------------------------
\subsection{Metallicity Validation}

@@
